% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2011 Jason R. Blevins
%           (C) 2012 Patrick O. Perry
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{geometry}

% BibTeX
\usepackage{natbib}
\usepackage{bibentry}

% Fonts
\usepackage[T1]{fontenc}
%\usepackage[urw-garamond]{mathdesign}
\usepackage{mathptmx}

\usepackage{hyperref}


% Set your name here
\def\name{Patrick O. Perry}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {statistics, applied statistics, networks, multivariate
    statistics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}
\nobibliography*

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  Department of Information, \\
  Operations, and Management Sciences \\
  Henry Kaufman Management Center \\
  44 West Fourth Street, Suite 8-63 \\
  New York, NY 10012-1125
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Phone: (212) 998-0194 \\
  Fax: (212) 995-4227 \\
  Email: pperry@stern.nyu.edu \\
  Homepage: \href{http://ptrckprry.com/}{http://ptrckprry.com}
\end{minipage}

%\section*{Summary of Achievements}
%
%\begin{itemize}
%  \item A
%  \item B
%  \item C
%\end{itemize}

\section*{Education}

\begin{itemize}
  \item Ph.D. Statistics, Stanford University, 2009.
    \begin{itemize}
    \item \textit{Dissertation:}
      Cross-Validation for Unsupervised Learning.
    \item \textit{Committee:}
      Art Owen (principal advisor), Trevor Hastie,
      Iain Johnstone, and Jonathan Taylor.
    \end{itemize}
  \item M.S. Electrical Engineering, Stanford University, 2004.
  \item B.S. Mathematics (Honors),
    Stanford University, 2003.
    \begin{itemize}
    \item \textit{Thesis:}
      Application of Simplicial Sets to Computational Topology.
    \item \textit{Supervisor:} Gunnar Carlsson.
    \end{itemize}
\end{itemize}

\section*{Experience}

\begin{itemize}
\item Assistant Professor, Department of Information, Operations, and
  Management Sciences, New York University Leonard N.~Stern School of Business,
  2011--Present.
\item Postdoctoral Fellow, School of Engineering and Applied Sciences, Harvard
  University, 2009--2011.
  \begin{itemize}
  \item \textit{Supervisor:} Patrick Wolfe.
  \end{itemize}
\end{itemize}


%\section*{Consulting}
%\begin{itemize}
%\item Littleton Joyce Ughetta Park \& Lelly LLP, New York, NY, 2012.
%    Review and critique expert witness testimony.
%\item Insignia Environmental, Palo Alto, CA, 2009.
%    Bootstrap-based analysis of three experiments designed to estimate
%    the environmental impact of installing new wind turbines in
%    Contra Costa County, in California.
%\item Kingsford Capital Management, Pt. Richmond, CA, 2008--2009.
%    General statistics advice, help with data analysis and programming in R.
%\item Stanford School of Medicine, Stanford, CA, 2006--2007.
%    Data analysis and reports for studies performed by resident
%    physicians under the supervision of Dr.~Raj Mitra, Orthopedic Surgery
%    Department.
%\end{itemize}




\section*{Publications}

\begin{itemize}
\item \bibentry{flynn2012consistent}.
\item \bibentry{perry2012null}.
\item \bibentry{perry2012point}.
\item \bibentry{allen2012singular}.
\item \bibentry{perry2011regularized}.
\item \bibentry{perry2010minimax}.
\item \bibentry{perry2010rotation}.
\item \bibentry{owen2009bcv}.
\item \bibentry{mitra2007efficacy}.
\end{itemize}





\section*{Teaching}

\subsection*{Instructor, NYU Stern}

\begin{itemize}

\item Statistics for Business Control and Regression and Forecasting Models
(Undergrad), Fall 2012.  65 students.
\textit{Instructor rating: 5.9/7.0; Course rating: 5.7/7.0.}

\item Regression and Forecasting Models (Undergrad), Spring 2012.  49
students.
\textit{Instructor rating: 6.1/7.0; Course rating: 5.6/7.0.}

\item Statistics for Business Control and Regression and Forecasting Models
(Undergrad), Spring 2012.  54 students.
\textit{Instructor rating: 5.7/7.0; Course rating: 5.4/7.0.}

\end{itemize}


\subsection*{Teaching Assistant, Stanford University}

\begin{itemize}
\item Spatial Statistics (Ph.D.), Spring 2009, taught by Jonathan Taylor.
\item Statistical Consulting Workshop, Winter 2009, taught by Rob Tibshirani.
\item Software for Data Analysis (Ph.D.), Winter 2008, taught by John Chambers.
\item Monte Carlo Methods (Ph.D.), Fall 2007, taught by Art Owen.
\item Modern Applied Statistics (Ph.D.), Fall 2006, taught by Trevor Hastie.
\item Statistical Consulting Workshop, Fall 2005, taught by Richard Olshen.
\item Statistical Computing (M.S.), Spring 2005, taught by Susan Holmes.
\end{itemize}

\section*{Presentations}
\subsection*{Conference Talks}
\begin{itemize}
\item Random Matrices and Statistical Applications.
  \textit{Joint Statistical Meetings (JSM)}.
  Montreal, Canada.
  August 5, 2013.
  Invited Session.

\item Modern Data Mining.
  \textit{30th Quality and Productivity Research Conference (QPRC)}.
  Niskayuna, NY.
  June 4--7, 2013.
  Invited Session.

\item Methods for Statistical Network Analysis: Beyond the Standard Paradigm.
  \textit{Joint Statistical Meetings (JSM)}.
  San Diego, CA.
  July 31, 2012.
  Invited Session.

\item Statistical Inference for Networks. 
  \textit{First conference of the International Society for NonParametric Statistics (ISNPS)}.
  Chalkidiki, Greece.
  June 15--19, 2012.
  Invited Session.

\item Statistical Analysis of Network Data.
  \textit{40th Annual Meeting of the Statistical Society of Canada (SSC)},
  Guelph, Canada.
  June 5, 2012.
  Invited Session.

\item The Analysis of Social Network Data in Public Health.
  \textit{Eastern North American Region/International Biometric Society (ENAR)}.
  Washington, DC.
  April 3, 2012.
  Invited Session.

\item Point process models for pairwise interaction data.
  \textit{Conference on Statistical Modeling and Inference for Networks (Statworks)}.
  Bristol, UK.
  June 30, 2010.
  Submitted Talk.

\item Community and homophily in a corporate e-mail network.
  \textit{New England Statistics Symposium (NESS)}.
  Cambridge, MA.
  April 17, 2010.
  Submitted Talk.

\item Cross validation for principal components.
  \textit{Banff International Research Station (BIRS) Program on Sparse Random Structures: Analysis and Computation}.
  Banff, Canada.
  January 28, 2010.
  Invited Talk.
\end{itemize}


\subsection*{Seminar Talks}

\begin{itemize}

\item Point process modeling for directed interactions
  \begin{itemize}
  \item University of Chicago, Department of Statistics, April 29, 2013.
  \item Cornell University, Department of Statistics, November 7, 2012.
  \item Penn State University, Department of Statistics, October 4, 2012.
  \item Columbia University, Department of Statistics, November 2, 2011.
  \item Harvard University, Institute of Quantitative Social Sciences, April 11, 2011.
  \item MIT, Department of Mathematics, February 11, 2011.
  \item NYU Stern, IOMS Department, February 8, 2011.
  \item University of Washington, Department of Statistics, January 28, 2011.
  \item % Point process models for repeated interaction data
    Harvard University, Department of Statistics, October 25, 2010.
  \item % Point process models for pairwise interaction data
    Stanford University, Department of Statistics, July 13, 2010.
  \item % A point process model for repeated interactions
    MIT Lincoln Laboratory Seminar, Lexington, MA, June 11, 2010.
  \end{itemize}


\item Cross validation for unsupervised learning
  \begin{itemize}
    \item Wharton School of the University of Pennsylvania, Department of Statistics,
      February 11, 2009. 
    \item 23andme, Mountain View, CA, January 22, 2009.
    \item Hewlett Packard Labs, Palo Alto, CA, September 26, 2008.
  \end{itemize}

\item Choosing how many principal components to keep
  \begin{itemize}
    \item Stanford University, Department of Statistics, April 14, 2009.
  \end{itemize}

\end{itemize}




\subsection*{Conference Posters}
\begin{itemize}
\item P.~O.~Perry and M.~W.~Mahoney.
  Regularized Laplacian estimation and fast eigenvector approximation.
  \textit{Twenty-Fifth Annual Conference on Neural Information Processing Systems (NIPS 2011)}.
  Granada, Spain.
  December 12, 2011.

\item P.~O.~Perry and P.~J.~Wolfe.
  Dual approaches to network science.
  \textit{Interdisciplinary Workshop on Information and Decision in Social Networks}.
  MIT, Cambridge, MA.
  May 31 -- June 1, 2011.

\item P.~O.~Perry and P.~J.~Wolfe.
  Point process models for pairwise interactions.
  \textit{SAMSI Program on Complex Networks Opening Workshop}.
  Research Triangle Park, NC.
  August 29 -- September 1, 2010.

\item P.~O.~Perry and A.~B.~Owen.
  Latent covariate detection and verification.
  \textit{Biomedical Computation at Stanford Symposium (BCATS)}.
  Stanford CA.
  October 21, 2006.

\item P.~O.~Perry and A.~B.~Owen.
  Latent covariate detection and verification: a case study in genetics.
  \textit{SAMSI Random Matrices Opening Workshop}.
  Research Triangle Park, NC.
  September 17--20, 2006.
\end{itemize}


\section*{Software}
\begin{itemize}
\item \href{http://cran.r-project.org/web/packages/RMTstat/index.html}
{\texttt{RMTStat} (http://cran.r-project.org)}.
With I.~Johnstone, Z.~Ma, and M.~Shahram.
Random matrix theory package for R.
%Distributions and statistics for high-dimensional covariance matrices.
2009.

\item \href{http://cran.r-project.org/web/packages/bcv/index.html}
{\texttt{bcv} (http://cran.r-project.org)}.
Bi-cross-validation package for R.
%Cross-validation-based rank selection for SVD approximations.
2009.

\item \href{http://hackage.haskell.org/cgi-bin/hackage-scripts/package/blas}
{\texttt{hs-blas} (http://hackage.haskell.org)}.
Linear algebra library for Haskell.
%Convenient interface to low-level BLAS and LAPACK libraries.
2008--2011.

\item \href{http://hackage.haskell.org/cgi-bin/hackage-scripts/package/monte-carlo}
{\texttt{hs-monte-carlo} (http://hackage.haskell.org)}.
Monte Carlo simulation library for Haskell.
%Random number distributions and sampling functions.
2008--2011.

\item \href{http://comptop.stanford.edu/programs/plex.html}
{\texttt{PLEX} (http://comptop.stanford.edu)}.
With V.\ de Silva.
Computational topology library for \textsc{MATLAB} and C++.
%Simplicial complexes and homology from point cloud data.
2006.

\end{itemize}



\section*{Professional Activities and Affiliations}
\begin{itemize}
\item Visiting Scholar, Institute for Quantitative Social Science, Harvard University, 2010--2011.
\item Member, NSA Statistical Advisory Group, Stanford University, 2010--2012.
\item Member, Geometrical/Spectral Analysis of Networks Working Group, SAMSI, 2010.
\item Member, American Statistical Association, 2011--Present.
\item Member, Institute of Mathematical Statistics, 2011--Present.
\item Reviewer for
  \textit{Annals of Applied Statistics},
  \textit{Annals of Statistics},
  \textit{Bernoulli},
  \textit{Biometrika},
  \textit{Chemometrics and Intelligent Laboratory Systems},
  \textit{Computational Statistics and Data Analysis},
  \textit{Electronic Journal of Statistics},
  \textit{Journal of the Royal Statistical Society (Series B)},
  \textit{Science},
  \textit{Statistical Science},
  \textit{Stochastic Processes and their Applications},
  \textit{Transactions on Pattern Analysis and Machine Intelligence}
\item Ph.D.~advisor for three students: Wen Cao, Cheryl Flynn, and Nikolay Kulmatitsky.
\end{itemize}




\section*{Grant Proposals}
\begin{itemize}
  \item Measuring, understanding, and responding to covert social networks.
  With P.~J.~Wolfe et al.
  Office of Naval Research MURI Award 58153-MA-MUR.
  2010.
\end{itemize}




%\section*{Honors, Awards, \& Fellowships}
\section*{Fellowships}

\begin{itemize}
\item Burt and Deedee McMurtry Stanford Graduate Fellowship, 2004--2007.
\end{itemize}

\medskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\bibliographystyle{plain}
\nobibliography{refs}

\end{document}
